Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-05 paper/aldebaran.tex
remove placeholder
new section; phrasing

@@

In order to detect the oscillations of Aldebaran via the radial velocity 
method we used the Hertzsprung SONG telescope \cite{2017ApJ...836..142G}. All 
observations were carried out in the highest resolution mode (R$\approx\,110.000$)
with an integration time of 30s. The observations were carried out between 27 September 
2016 and  12 January 2017, during this time we attempted to obtain at least one 
visit per available night. A total of 254 spectra was obtained. The spectra were
extracted using the SONG pipeline (see \cite{2017ApJ...836..142G}). SONG employs an iodine cell for
precise wavelength calibration and the velocities were determined using the $\it iSONG$
software following the same procedures as described in \cite{2017ApJ...836..142G}.   The typical
velocity precision per visit is 2.5$m\,s^{-1}$ allowing us to easily detect the oscillations
which displays a peak-to-peak amplitude of $\approx \, 170 \, \rm m \, s^{-1}$. $\bf Figure XX$ show
the radial velocities obtained -- oscillations are easily visible as well as a long-term
trend. This is probably due to the a manifestation of the planetary companion reported by
\cite{Hatzes2015}.

@@

With the determination of the stellar mass it is possible to infer the parameters Aldebaran had while it was on the main sequence. We conduct a Monte Carlo simulation, drawing masses randomly from a Gaussian distribution $M \sim \mathcal{N}(1.16,0.07)$ and metallicities $[\text{Fe}/\text{H}] \sim \mathcal{N}(-0.15,0.2)$ \citep{decin2003} to predict the luminosity of the main-sequence progenitor, and the semi-major axis of the planet's orbit.  %Using the scaling relations of \citep{eker2015}, we find that Aldebaran would have had a luminosity $L_* = 2.0 \pm 0.37~\lsun$ on the main sequence.  
Using the Mesa Isochrones and Stellar Tracks \citep[MIST:][]{mist0,mist1} models via the \textsc{isochrones} package \citep{isochrones}, we compute the evolution of the luminosity $L$ of the star along the main sequence; $L$ evolves from $2.0 \pm 0.7$~\lsun at 0.5~Gyr to $3.5 \pm 2.3$~\lsun at 4.5~Gyr. 
We note that this implies that the planet at a semi-major axis of $1.50\, \pm\, 0.03$~AU would have been subject to an insolation comparable to that of the Earth, evolving from 0.5~Gyr to 4.5~Gyr from $0.86\, \pm\, 0.27$ to $1.55 \,\pm\,1.0$ times that of the Earth today (Figure~\ref{insolation}). Subject as well as this to the great uncertainties of the planet's orbital evolution and albedo, Aldebaran~b and any of its moons (or its S-type planets if it is a brown dwarf) may well have hosted temperate environments for some of their history, now long-since destroyed by their star's evolution away from the main sequence.

@@

We thank the academy....

>>>>

\subsection{Archival Observations}

@@

In order to confirm the oscillations detected in the archival data, we used the Hertzsprung SONG telescope \cite{2017ApJ...836..142G} to conduct high time cadence follow-up observations. These were carried out in the highest resolution mode (R$\approx\,110.000$)
with an integration time of 30s, between 27 September 
2016 and  12 January 2017. During this time we attempted to obtain at least one 
visit per available night, for a total of 254 epochs over the campaign. The spectra were
extracted using the SONG pipeline (see \cite{2017ApJ...836..142G}). SONG employs an iodine cell for
precise wavelength calibration and the velocities were determined using the $\it iSONG$
software following the same procedures as described in \cite{2017ApJ...836..142G}.   The typical
velocity precision per visit is 2.5$m\,s^{-1}$ allowing us to easily detect the oscillations
which displays a peak-to-peak amplitude of $\approx \, 170 \, \rm m \, s^{-1}$. $\bf Figure XX$ show
the radial velocities obtained -- oscillations are easily visible as well as a long-term
trend. This is probably due to the a manifestation of the planetary companion reported by
\cite{Hatzes2015}.

@@

With the determination of the stellar mass it is possible to infer the parameters Aldebaran had while it was on the main sequence. We conduct a Monte Carlo simulation, drawing masses randomly from a Gaussian distribution $M \sim \mathcal{N}(1.16,0.07)$ and metallicities $[\text{Fe}/\text{H}] \sim \mathcal{N}(-0.15,0.2)$ \citep{decin2003} to predict the luminosity of the main-sequence progenitor, and the semi-major axis of the planet's orbit.  
Using the Mesa Isochrones and Stellar Tracks \citep[MIST:][]{mist0,mist1} models via the \textsc{isochrones} package \citep{isochrones}, we compute the evolution of the luminosity $L$ of the star along the main sequence; $L$ evolves from $2.0 \pm 0.7$~\lsun at 0.5~Gyr to $3.5 \pm 2.3$~\lsun at 4.5~Gyr. 
We note that this implies that the planet at a semi-major axis of $1.50\, \pm\, 0.03$~AU would have been subject to an insolation comparable to that of the Earth, evolving from 0.5~Gyr to 4.5~Gyr from $0.86\, \pm\, 0.27$ to $1.55 \,\pm\,1.0$ times that of the Earth today (Figure~\ref{insolation}). Subject as well as this to the great uncertainties of the planet's orbital evolution and albedo, Aldebaran~b and any of its moons (or its S-type planets if it is a brown dwarf) may well have hosted temperate environments for some of their history, now long-since destroyed by their star's evolution away from the main sequence.

@@
